### 2012-05-18 inst/examples/cost_of_bias.Rmd
cost of bias baseline against known bias

We calculate the stochastic transition matrix for the probability of going from any state \\(x_t \\) to any other state \\(x_{t+1}\\) the following year, for each possible choice of harvest \\( h_t \\).  This provides a look-up table for the dynamic programming calculations. In the Sethi case, computing the distribution over multiple sources of noise is actually quite difficult.  Simulation turns out to be more efficient than numerically integrating over each distribution.  We use this matrix to compute the optimum strategy for all possible states of the world by dynamic programming, and then simulate replicates while applying this rule.

@@

```{r}
set.seed(42)
sims_three <- lapply(1:100, function(i){
  est_pars[1] <- rnorm(1, pars[1], par_var)
  ForwardSimulate(f, est_pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````

## Unbiased error in growth estimate

```{r}
sigma_g <- sqrt(0.15^2 + par_var^2)   # Noise in population growth
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1 
z_i <- function() 1 
````

We will compare this result to the situation of underestimating the uncertainty in the growth rate, but knowning the parameter exactly.  We use the deterministic optimum solution under a reality that has log-normal growth noise equal to the sum of the variances in the previous example, \( \sigma_g = \)  `r sigma_g`.

```{r}
set.seed(42)
sims_four <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, det_opt$D, z_g, z_m, z_i, profit)
})
````

@@

```{r tidy}
sims <- list(known = sims_one, Growth = sims_two, Bias = sims_three, Underestimate = sims_four)

@@

Summary statistics tell the final story:

@@

>>>>

We calculate the stochastic transition matrix for the probability of going from any state \\(x_t \\) to any other state \\(x_{t+1}\\) the following year, for each possible choice of harvest \\( h_t \\).  This provides a look-up table for the dynamic programming calculations.

@@

```{r}
set.seed(42)
bias <- rnorm(100, pars[1], par_var)
sims_three <- lapply(1:100, function(i){
  est_pars[1] <- bias[i]
  ForwardSimulate(f, est_pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````

## Known bias

The correct baseline comparison against the above scenario, Mike points out to me, still includes the bias, but solves for the optimal solution of that random draw.  This is much slower since it requires solving a new optimum each time, but parallelizes well.

```{r}
require(snowfall)
sfInit(parallel=T, cpu=16)
sfLibrary(pdgControl)
sfExportAll()
sims_four <- sfLapply(1:100, function(i){
  est_pars[1] <- bias[i] 
  SDP_Mat <- determine_SDP_matrix(f, est_pars, x_grid, h_grid, sigma_g )
  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
                     profit, delta=0.05, reward=0)
  ForwardSimulate(f, est_pars, x_grid, h_grid, x0=K, det_opt$D, z_g, z_m, z_i, profit)
})
````

@@

```{r tidy}
sims <- list(known = sims_one, Growth = sims_two, RandomBias = sims_three, KnownBias = sims_four)

@@

Summary statistics

@@

```{r }
save(list="dt", file="bias.rda")
````

Direct comparisons:

```{r echo=TRUE}
setkey(dt, uncertainty)
cost_of_bias = dt[knownBias, sum(profit), by=reps]$V1 - dt[randomBias, sum(profit), by=reps]$V1
cost_of_bias
mean(cost_of_bias)
sd(cost_of_bias)
````

### 2012-05-18 inst/examples/policycosts/stochastic_norms.Rmd
cost of bias baseline against known bias

# Policy Costs 
 * author Carl Boettiger, <cboettig@gmail.com>
 * license: CC0

@@

``` {r policycost_optim }
c2 <- 4.0
penalty <- fixed(c2)
policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                    profit, delta, reward, penalty = penalty)
cache=FALSE
````

>>>>

# Policy Costs Baseline 
 * author Carl Boettiger, <cboettig@gmail.com>
 * license: CC0

@@

``` {r policycost_optim }
c2 <- 0.0
penalty <- L1(c2)
policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                    profit, delta, reward, penalty = penalty)
cache=FALSE
````
